---
title: "IL33_HiBiT"
author: "Li Chengchen (Cherry)"
date: "2025-04-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(ggbreak)
library(rstatix)
library(dplyr)
library(forcats)
```

# HiBiT IL-33  

- Genetically modified N/TERT keratinocyte cell lines were utilized for Nano-Glo HiBiT experiments. This N/TERT cell lines contained a 33 nucleotide HiBiT tag directly adjacent to the IL1B and IL33 genes. 

```{r}
il33 <- readxl::read_excel(
  "~/ASMP_Dermotype/Data/5_experiment/IL-33_HiBiT_from_Stephen.xlsx", 
  sheet = 1)
names(il33) <- c("strain", "Rep 1", "Rep 2", "Rep 3", "runs") 
il33_tmp <- il33 %>% 
  pivot_longer(cols= c("Rep 1", "Rep 2", "Rep 3"), 
               names_to = "id", 
               values_to = "IL33") %>% 
  mutate(runs = as.character(runs))
```

- calculate the relative fold change in luminescence measurements using the reference group (treated with BHI only)

```{r cars}
il33_norm <- il33_tmp %>%
  filter(strain == "Untreated") %>%
  select(id, runs, IL33_Untreated = IL33) %>%
  right_join(il33_tmp, by = c("id", "runs")) %>%
  mutate(IL33_normalized = IL33 / IL33_Untreated) %>% 
  select(-IL33) %>% 
  rename(., c("IL33" = "IL33_normalized")) %>% 
  mutate(
         strain1 = strain) %>% 
  separate(strain1, into = c("C1", "C2", "C3", "C4", "C5"), sep = " ") %>% 
  mutate(species = C2) %>% 
  mutate(species = case_when(is.na(species) ~ "Untreated", 
                             str_detect(species, "SH") ~ "S. hominis",
                             str_detect(species, "SE") ~ "S. epidermidis",
                             str_detect(species, "Mluteus") ~ "M. luteus",
                             
                             # str_detect(species, "war") ~ "S. warneri", 
                             # str_detect(species, "cap") ~ "S. capitis", 
                             T~species)) %>% 
  mutate(species = factor(species, levels = c("Untreated","TritonX", "BHI",  "M. luteus",  "S. hominis", "S. epidermidis"))) %>% 
  group_by(strain, runs) %>% 
  mutate(ave_IL33 = mean(IL33, na.rm = T)) %>% 
  ungroup() 
#%>% filter(strain != "5% SE 09-81 (S4, AX) Supernatant")
```

```{r, echo=FALSE}
results <- il33_norm %>%
  wilcox_test(IL33 ~ strain, ref.group = "5% BHI"
              , alternative = "less"
              ) %>% 
  adjust_pvalue(method = "BH") %>% 
  add_significance()

annotation_data <- il33_norm %>%
  distinct(species, strain ) %>%       # Get unique species-group combinations
  left_join(results, join_by("strain" == "group2"))   # Attach p-values


y_pos <- il33_norm %>%
  group_by(species) %>%
  summarise(y_pos = max(IL33, na.rm = TRUE)*1.01) %>%
  ungroup() %>% 
  left_join(annotation_data, by = c("species"))

# Reorder `strain` within each `species` by median IL33
strain_order <- il33_norm %>%
  group_by(species, strain) %>%
  summarise(median_IL33 = median(IL33, na.rm = TRUE), .groups = "drop") %>%
  arrange(species, median_IL33) %>%
  group_by(species) %>%
  mutate(strain_ordered = factor(strain, levels = unique(strain)))

il33_norm <- il33_norm %>%
  left_join(strain_order[, c("species", "strain", "strain_ordered")], by = c("species", "strain"))
```


## visualization and statistical test between each isolate (averaged technical replicates)

```{r, echo=FALSE}
ave_il33_norm <- il33_norm %>%
  distinct(species, strain, runs, ave_IL33)

results <- ave_il33_norm %>%
  distinct(species, strain, runs, ave_IL33) %>% 
  mutate(stat_group = case_when(species %in% c("M. luteus", "BHI") ~ "Ref", 
        T~strain)) %>% 
  wilcox_test(ave_IL33 ~ stat_group, ref.group = "Ref"
              , alternative = "less"
              ) %>% 
  adjust_pvalue(method = "BH") %>% 
  add_significance(
      cutpoints = c(0, 1e-04, 0.001, 0.01, 0.05, 1),
      symbols = c("****", "***", "**", "*", "")
  )


annotation_data <- ave_il33_norm %>%
  distinct(species, strain ) %>%       # Get unique species-group combinations
  left_join(results, join_by("strain" == "group2")) %>% 
  filter(strain!="Untreated") # Attach p-values


y_pos <- ave_il33_norm %>%
  filter(strain!="Untreated") %>% 
  group_by(species) %>%
  summarise(y_pos = max(ave_IL33, na.rm = TRUE)*1.01) %>%
  ungroup() %>% 
  left_join(annotation_data, by = c("species")) 

# Reorder `strain` within each `species` by median IL33
strain_order <- ave_il33_norm %>%
  filter(strain!="Untreated") %>% 
  group_by(species, strain) %>%
  summarise(median_ave_IL33 = median(ave_IL33, na.rm = TRUE), .groups = "drop") %>%
  arrange(species, median_ave_IL33) %>%
  group_by(species) %>%
  mutate(strain_ordered = factor(strain, levels = unique(strain)))

ave_il33_norm <- ave_il33_norm %>%
  left_join(strain_order[, c("species", "strain", "strain_ordered")], by = c("species", "strain"))

# Now plot using the reordered `strain_ordered`
p1 <- ave_il33_norm %>% 
  filter(strain!="Untreated") %>% 
  ggplot(aes(x = strain_ordered, y = ave_IL33)) +
  geom_boxplot(outliers = FALSE) +
  geom_jitter(width = 0.2, alpha = 0.7) +
  facet_grid(~species, scales = "free_x", space = "free_x",  labeller = label_wrap_gen(width = 2)) +
  ggpubr::theme_pubr(x.text.angle = 45) +
  geom_text(
    data = y_pos,
    aes(x = strain, y = y_pos, label = p.adj.signif),
    vjust = -0.5, size = 5, color = "red"
  ) +
  labs(x = "", y = "pro-IL-33 relative light units ") +
  coord_cartesian(ylim = c(0, max(il33_norm$ave_IL33, na.rm = TRUE) * 1.15))

p1
```

```{r, exclude = F}
p1 <- p1 +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x.bottom = element_blank(),
    axis.text.y.right = element_blank(),
    strip.text = element_text(face = c("bold.italic"), size = 7)
  )
p1
```


