---
title: "plot_da_network"
output: html_document
date: '2023-11-20'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(ggh4x)
library(dplyr)
library(openxlsx)
library(tidyr)
library(igraph)
wb <- loadWorkbook("~/ASMP_Dermotype/Data/3_assoc_diff/co_occurence_result.xlsx")
load("~/ASMP_Dermotype/Data/3_assoc_diff/net_derm_ax.RData")
load("~/ASMP_Dermotype/Data/3_assoc_diff/all_networks_noax_29nov.RData")
source('~/ASMP_Dermotype/Script/Analysis/utils_network_asmp.R')
```

```{r}
sheet_names <- names(wb)
df_list <- lapply(sheet_names, function(sheet) {
  read.xlsx(wb, sheet = sheet)
})
names(df_list) <- sheet_names
df_list <- lapply(df_list, function(df) {
  colnames(df) <- c("Taxa1", "Taxa2", "Cor1", "Cor2", "Padj")
  df
})

assoMat_ac<- data.frame(df_list$Ac_CCREPE)
assoMat_vf<- data.frame(df_list$Vf_CCREPE)
assoMat_ub<- data.frame(df_list$Ub_CCREPE)
assoMat_fo<- data.frame(df_list$Fo_CCREPE)
assoMat_ps<- data.frame(df_list$Ps_CCREPE)
assoMat_sc<- data.frame(df_list$Sc_CCREPE)
assoMat_ax<- data.frame(df_list$Ax_CCREPE)

combined_network <- rbind(assoMat_ac %>% mutate(Site = 'Ac'),
                          assoMat_vf %>% mutate(Site = 'Vf'),
                          
                          assoMat_ub %>% mutate(Site = 'Ub'),
                          assoMat_fo %>% mutate(Site = 'Fo'),
                          
                          assoMat_ps %>% mutate(Site = 'Ps'),
                          assoMat_sc %>% mutate(Site = 'Sc'),
                          assoMat_ax %>% mutate(Site = 'Ax'))

 oral <- c('S. mitis oralis pneumoniae', 'S. salivarius', 'R. dentocariosa',
           'V. parvula', 'C. matruchotii', 'R. aeria', 'C. durum',
           'A. viscosus', 'R. mucilaginosa', 'P. melaninogenica',
           'S. sanguinis', "N. flavescens", "A. massiliensis")
 corynebact <- c('C. tuberculostearicum', 'C. pseudogenitalium',
                 'C. kroppenstedtii', 'C. accolens', 'C. jeikeium', 'C. durum', 'C. matruchotii')
 staph <- c('S. hominis', 'S. epidermidis', 'S. haemolyticus', 'S. saprophyticus',
            'S. caprae capitis')
 cuti <- c('C. acnes', 'C. avidum', 'C. granulosum')
 malass <- c('M. restricta', 'M. furfur', 'M. globosa', 'M. japonica', 'M. dermatis', 'M. sloofiae')
 strep <- c('S. mitis oralis pneumoniae', 'S. salivarius', 'S. sanguinis')
 rothia <- c('R. dentocariosa','R. aeria','R. mucilaginosa')
 microco <- c('M. luteus')
 morax <- c('M. osloensis')

 common_skin <- 'Corynebacterium\nStaphylococcus\nMalassezia'
 oral_skin <- 'Streptococcus\nRothia\nCorynebacterium\nPrevotella\nActinomyces\nVeilonella'

# add category for better visualization
combined_network <- combined_network %>%
  mutate(Category = case_when((Taxa1 %in% oral) & (Taxa2 %in% oral)~ oral_skin,
                           grepl('acnes', Taxa1) ~ 'C. acnes',
                           grepl('acnes', Taxa2) ~ 'C. acnes',
                           (Taxa1 %in% c(corynebact, staph, malass, microco, morax)) &
                           (Taxa2 %in% c(corynebact, staph, malass, microco, morax)) ~ common_skin,
                           TRUE ~ 'Others'))
p_filt <- 0.1
combined_network_filt <- combined_network %>% 
    tidyr::unite(Interaction, c("Taxa1", "Taxa2"), sep = '-') %>% 
    #mutate(Interaction = rearrange_names(Interaction)) %>% 
  filter(Padj <p_filt) %>% 
  dplyr::select(-Padj)
```

# check the number of unique nodes and edges in each networks 
```{r}
network_node_sum <- combined_network %>% 
  select(Site, Taxa1, Taxa2) %>% 
  reshape2::melt(id = "Site") %>% 
  group_by(Site) %>% 
  summarize(n_node = n_distinct(value))

network_edge_sum <- combined_network %>% 
  group_by(Site) %>% 
  summarise(n_edge_1 = sum(Cor1 != 0), 
            n_edge_2 = sum(Cor2 != 0)) %>% 
  reshape2::melt(id = "Site")
```

# check the proportion of shared edges 

```{r}
combined_network  <-  combined_network %>%
  mutate(Group = 
         case_when(
                  Cor1*Cor2 > 0 & Padj <=p_filt ~ "Strength_variant", 
                  Cor1*Cor2 < 0 & Padj <=p_filt~ "Reverse", 
                  Cor1*Cor2 == 0 & Padj <=p_filt ~ "Exclusive", 
                  Padj >p_filt ~ "Non-differential",
                  T ~ NA))
df_diff_prop <-  combined_network %>% 
  group_by(Site) %>%
  dplyr::summarize(
          Total = n(),
          Reverse_n = sum(Group == "Reverse"), 
          Strength_variant_n = sum(Group == "Strength_variant"), 
          Exclusive_n = sum (Group == "Exclusive"), 
          Differential_n = sum(Group %in% c("Reverse", "Strength_variant", "Exclusive"))) %>% 
  mutate(Site = factor(Site, levels = c("Ax", "Ac", "Vf", "Ub", "Fo", "Ps", "Sc"))) %>% 
  mutate(Site_n = paste(Site, "\n(n = ", Total, ")", sep = ""),
         Differential = Differential_n /Total,
         Non_Differential = 1-Differential_n /Total, 
         Reverse = Reverse_n / Differential_n,
         Strength_variant = Strength_variant_n  / Differential_n,
         Exclusive = Exclusive_n / Differential_n) %>% 
  arrange(Site)

order <- df_diff_prop$Site_n


p <- df_diff_prop %>% 
  select(Site_n, Non_Differential, Differential) %>%  
  reshape2::melt() %>%
  data.frame() %>%
  mutate(Site_n = forcats::fct_relevel(Site_n, order)) %>%
  ggplot(., aes(fill = variable, y= value, x= Site_n)) + 
      geom_bar(position="fill", stat="identity") +
  scale_fill_manual(values = c("grey", "maroon")) +
  scale_y_continuous(labels = scales::percent) +
  ggpubr::theme_pubr(base_size = 7) +
  theme(legend.title = element_blank(),
        legend.position = "top",
        axis.title = element_blank())
p
```


# Check which differential edges are between core species 

```{r}
diff_edge_delta <- combined_network  %>% 
  filter(Padj < p_filt) %>% 
  mutate(delta = abs(Cor1-Cor2)) %>% 
  #group_by(Site) %>% 
  arrange(Site, desc(delta))
diff_edge_delta_list <- split (diff_edge_delta, diff_edge_delta$Site)


# load core species previously identified for each site and dermotype 
load("~/ASMP_Dermotype/Data/2_basic/HighPrev_site.RData")
d_all_site <- d_all %>% dplyr::rename(Category = Site)
load("~/ASMP_Dermotype/Data/2_basic/HighPrev_Dermotype.RData")
d_all_dermotype <- d_all %>% 
  dplyr::rename(Category = Dermotype)
d_Category <- rbind(d_all_site, d_all_dermotype) %>% 
  mutate(Taxa_short = gsub("^s__", "", Taxa_og)) %>% 
  mutate(Taxa_short = gsub("^([A-Za-z])[^_]+_", "\\1. ",  Taxa_short)) %>% 
  mutate(Taxa_short = gsub("_", " ", Taxa_short)) %>% 
  mutate(Site = gsub("\\-.*", "", Category))
core_species_list <- split(d_Category, d_Category$Site)

core_species_edge_list <- list()
for (i in unique(names(diff_edge_delta_list))) {
  core_species_df <- core_species_list[[i]] %>% data.frame()
  edge_df <- diff_edge_delta_list[[i]] %>% data.frame() %>% 
    mutate(edge_btw_core_species = case_when(Taxa1 %in% core_species_df$Taxa_short &
                                             Taxa2 %in% core_species_df$Taxa_short ~ "Y",
           T ~ "N"))
  core_species_edge_list[[i]] <- edge_df
}

all_edges <- do.call(rbind, core_species_edge_list) 
table(all_edges$edge_btw_core_species)
```

# visualize the proportion of differential edges that are between core species for each skin site (the number of diff edges between 2 core species / the total number of diff edges)

```{r}
core_edge_prop <- all_edges %>% 
  group_by(Site) %>% 
  summarize(core_edge_n = sum (edge_btw_core_species == "Y"),
         diff_edge_n = n(), 
         diff_edge_btw_core = core_edge_n / diff_edge_n, 
         diff_edge_btw_non_core = 1- core_edge_n / diff_edge_n) %>% 
  ungroup() %>% 
  distinct(Site, diff_edge_btw_core, diff_edge_btw_non_core) %>% 
  reshape2::melt() %>%
  data.frame() 

order3  <- df_diff_prop$Site

p_core_edge_prop <- core_edge_prop %>%
  mutate(Site = forcats::fct_relevel(Site, as.character(order3)),
         variable = forcats::fct_relevel(variable, 
                                c("diff_edge_btw_non_core", "diff_edge_btw_core"))) %>% 
  ggplot(., aes(fill = variable, y= value, x= Site)) + 
  geom_bar(position="fill", stat="identity") +
  scale_fill_manual(values = c( "#676765", "#FFB902")) +
  scale_y_continuous(labels = scales::percent) +
  ggpubr::theme_pubr(base_size = 7, legend = "top") +
  theme(legend.title = element_blank(),
        axis.title = element_blank())
p_core_edge_prop 
```


# visualize the top 5 most different core species edges for each site 

```{r}
core_species_edge <- all_edges %>% 
  filter(edge_btw_core_species == "Y") %>% 
  arrange(Site, desc(delta)) %>% 
  mutate(core_species_pair = paste(Taxa1, Taxa2, sep = "-")) 

core_species_edge_top5 <- core_species_edge %>%
  arrange(Site, desc(delta)) %>%
  group_by(Site) %>%
  slice_head(n = 5) %>% 
  mutate(Rank = rank(-delta, ties.method = "min")) %>% 
  ungroup() %>%
  tidyr::gather(key = "Correlation_Type", value = "Correlation", Cor1, Cor2) %>%
  mutate(Correlation_Type = factor(Correlation_Type, levels = c("Cor1", "Cor2", "delta")))

core_species_edge_top5_group <- core_species_edge_top5 %>%
  group_by(core_species_pair) %>% 
  summarise(ave_rank = mean(Rank, na.rm = T),
            total_times = n()) %>% 
  arrange(desc(total_times), ave_rank)


core_species_edge_top5 <- core_species_edge_top5 %>% 
  mutate(core_species_pair = factor(core_species_pair, 
                            levels = core_species_edge_top5_group$core_species_pair)) %>% 
  mutate(Site = factor(Site, levels = c("Ax", "Ac", "Vf", "Ub", "Fo", "Sc")))

p_top5_core_species_edge <- ggplot(core_species_edge_top5, 
                                   aes(x = Correlation_Type, y = core_species_pair)) +
  geom_tile(aes(fill = Correlation), color = "white") +
  scale_fill_gradient2(low = "orange", mid = "white", high = "purple", name = "Correlation") +
  scale_y_discrete(limits=rev) + 
  facet_grid(~ Site) +  
  ggpubr::theme_pubr(base_size = 12, x.text.angle = 30, border = T) +
  theme(axis.title = element_blank(), 
        legend.position = "left", 
        legend.direction = "vertical", 
        axis.text.y = element_text(face = "italic"))
p_top5_core_species_edge 
```


## VF
```{r}
attr_vf_1 <- generate_nodes_edges(assoMat_vf, 'Cor1')
sub.g.vf.1 <- modif_graph(attr_vf_1)

attr_vf_2 <- generate_nodes_edges(assoMat_vf, 'Cor2')
sub.g.vf.2 <- modif_graph(attr_vf_2)

# #----------find the proper coordinates -----------#
# set.seed(1)
# tkplot(sub.g.vf.1,
#      edge.width = E(sub.g.vf.1)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.vf.1),
#      #layout = coords,
#      vertex.size = set_nodesize(net_derm_vf$normCounts1, sub.g.vf.1),
#      vertex.shape = ifelse(V(sub.g.vf.1)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # 
# tkplot(sub.g.vf.2,
#      edge.width = E(sub.g.vf.2)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.vf.2),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_vf$normCounts2, sub.g.vf.2),
#      vertex.shape = ifelse(V(sub.g.vf.2)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.2,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # 
# # coords <- tk_coords(24)
# # write_tsv(data.frame(coords), './assoc_diff/vf_coords.tsv')


#--------plot them------------#
coords <- read_tsv('./assoc_diff/vf_coords.tsv') %>% as.matrix()
svg(file="./vf-network.svg", width=16, height=7)
par(mfrow=c(1,2), mar=c(0,0,0,1))
plot(sub.g.vf.1,
     edge.width = E(sub.g.vf.1)$weight,
     # layout = layout.fruchterman.reingold(sub.g.vf.1),
     layout = coords,
     vertex.size = set_nodesize(net_derm_vf$normCounts1, sub.g.vf.1),
     vertex.shape = ifelse(V(sub.g.vf.1)$label %in% oral, "square", "circle"),
     vertex.label.dist=1.1,
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black"
     )

plot(sub.g.vf.2, 
     edge.width = E(sub.g.vf.2)$weight,
     # layout = layout.fruchterman.reingold(sub.g.vf.2),
     layout = coords,
     vertex.size = set_nodesize(net_derm_vf$normCounts2, sub.g.vf.2),
     vertex.shape = ifelse(V(sub.g.vf.1)$label %in% oral, "square", "circle"), 
     vertex.label.dist=1.1, 
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
     )
dev.off()
```


## UB

```{r}
attr_ub_1 <- generate_nodes_edges(assoMat_ub, 'Cor1')
sub.g.ub.1 <- modif_graph(attr_ub_1)

attr_ub_2 <- generate_nodes_edges(assoMat_ub, 'Cor2')
sub.g.ub.2 <- modif_graph(attr_ub_2)

# # #----------find the proper coordinates -----------#
# set.seed(1)
# tkplot(sub.g.ub.1,
#      edge.width = E(sub.g.ub.1)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.ub.1),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_ub$normCounts1, sub.g.ub.1),
#      vertex.shape = ifelse(V(sub.g.ub.1)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # 
# tkplot(sub.g.ub.2,
#      edge.width = E(sub.g.ub.2)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.ub.2),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_ub$normCounts2, sub.g.ub.2),
#      vertex.shape = ifelse(V(sub.g.ub.2)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # 
# coords <- tk_coords(12)
# write_tsv(data.frame(coords), './assoc_diff/ub_coords.tsv')
#--------plot them------------#
coords <- read_tsv('./assoc_diff/ub_coords.tsv') %>% as.matrix()
svg(file="./ub-network.svg", width=16, height=7)
par(mfrow=c(1,2), mar=c(0,0,1,0))
plot(sub.g.ub.1,
     edge.width = E(sub.g.ub.1)$weight,
     # layout = layout.fruchterman.reingold(sub.g.ub.1),
     layout = coords,
     vertex.size = set_nodesize(net_derm_ub$normCounts1, sub.g.ub.1),
     vertex.shape = ifelse(V(sub.g.ub.1)$label %in% oral, "square", "circle"),
     vertex.label.dist=1.1,
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
     main = "Ub-1"
     )

plot(sub.g.ub.2, 
     edge.width = E(sub.g.ub.2)$weight,
     # layout = layout.fruchterman.reingold(sub.g.ub.2),
     layout = coords,
     vertex.size = set_nodesize(net_derm_ub$normCounts2, sub.g.ub.2),
     vertex.shape = ifelse(V(sub.g.ub.1)$label %in% oral, "square", "circle"), 
     vertex.label.dist=1.1, 
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
      main = "Ub-2"
     )
dev.off()
```

## FO
```{r}
attr_fo_1 <- generate_nodes_edges(assoMat_fo, 'Cor1')
sub.g.fo.1 <- modif_graph(attr_fo_1)

attr_fo_2 <- generate_nodes_edges(assoMat_fo, 'Cor2')
sub.g.fo.2 <- modif_graph(attr_fo_2)

# # #----------find the proper coordinates -----------#
# set.seed(1)
# tkplot(sub.g.fo.1,
#      edge.width = E(sub.g.fo.1)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.fo.1),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_fo$normCounts1, sub.g.fo.1),
#      vertex.shape = ifelse(V(sub.g.fo.1)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # # 
# tkplot(sub.g.fo.2,
#      edge.width = E(sub.g.fo.2)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.fo.2),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_fo$normCounts2, sub.g.fo.2),
#      vertex.shape = ifelse(V(sub.g.fo.2)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # 
#coords <- tk_coords(19)
#write_tsv(data.frame(coords), './assoc_diff/fo_coords.tsv')
#--------plot them------------#
coords <- read_tsv('./assoc_diff/fo_coords.tsv') %>% as.matrix()
svg(file="./fo-network.svg", width=16, height=6)
par(mfrow=c(1,2), mar=c(0,0,1,0))
plot(sub.g.fo.1,
     edge.width = E(sub.g.fo.1)$weight,
     layout = coords,
     vertex.size = set_nodesize(net_derm_fo$normCounts1, sub.g.fo.1),
     vertex.shape = ifelse(V(sub.g.fo.1)$label %in% oral, "square", "circle"),
     vertex.label.dist=1.1,
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
     main = "Fo-1"
     )

plot(sub.g.fo.2, 
     edge.width = E(sub.g.fo.2)$weight,
     layout = coords,
     vertex.size = set_nodesize(net_derm_fo$normCounts2, sub.g.fo.2),
     vertex.shape = ifelse(V(sub.g.fo.1)$label %in% oral, "square", "circle"), 
     vertex.label.dist=1.1, 
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
      main = "Fo-2"
     )
dev.off()

```

## SC
```{r}
attr_sc_1 <- generate_nodes_edges(assoMat_sc, 'Cor1')
sub.g.sc.1 <- modif_graph(attr_sc_1)

attr_sc_2 <- generate_nodes_edges(assoMat_sc, 'Cor2')
sub.g.sc.2 <- modif_graph(attr_sc_2)

# # # #----------find the proper coordinates -----------#
# set.seed(1)
# tkplot(sub.g.sc.1,
#      edge.width = E(sub.g.sc.1)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.sc.1),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_sc$normCounts1, sub.g.sc.1),
#      vertex.shape = ifelse(V(sub.g.sc.1)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # # # 
# tkplot(sub.g.sc.2,
#      edge.width = E(sub.g.sc.2)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.sc.2),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_sc$normCounts2, sub.g.sc.2),
#      vertex.shape = ifelse(V(sub.g.sc.2)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # # 
# coords <- tk_coords(24)
# write_tsv(data.frame(coords), './assoc_diff/sc_coords.tsv')
#--------plot them------------#
coords <- read_tsv('./assoc_diff/sc_coords.tsv') %>% as.matrix()
svg(file="./sc-network.svg", width= 10, height= 4)
par(mfrow=c(1,2), mar=c(0,0,1,1))
plot(sub.g.sc.1,
     edge.width = E(sub.g.sc.1)$weight,
     layout = coords,
     vertex.size = set_nodesize(net_derm_sc$normCounts1, sub.g.sc.1),
     vertex.shape = ifelse(V(sub.g.sc.1)$label %in% oral, "square", "circle"),
     vertex.label.dist=1.1,
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
     main = "Sc-1"
     )

plot(sub.g.sc.2, 
     edge.width = E(sub.g.sc.2)$weight,
     layout = coords,
     vertex.size = set_nodesize(net_derm_sc$normCounts2, sub.g.sc.2),
     vertex.shape = ifelse(V(sub.g.sc.1)$label %in% oral, "square", "circle"), 
     vertex.label.dist=1.1, 
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
      main = "Sc-2"
     )
dev.off()
```

## AX
```{r}
attr_ax_1 <- generate_nodes_edges(assoMat_ax, 'Cor1')
sub.g.ax.1 <- modif_graph(attr_ax_1)

attr_ax_2 <- generate_nodes_edges(assoMat_ax, 'Cor2')
sub.g.ax.2 <- modif_graph(attr_ax_2)

# # #----------find the proper coordinates -----------#
# set.seed(1)
# tkplot(sub.g.ax.1,
#      edge.width = E(sub.g.ax.1)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.ax.1),
#      layout = coords,
#      vertex.size = set_nodesize(net_derm_ax$normCounts1, sub.g.ax.1),
#      vertex.shape = ifelse(V(sub.g.ax.1)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.1,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # 
# tkplot(sub.g.ax.2,
#      edge.width = E(sub.g.ax.2)$weight,
#      #layout = layout.fruchterman.reingold(sub.g.ax.2),
#      #layout = coords,
#      vertex.size = set_nodesize(net_derm_ax$normCounts2, sub.g.ax.2),
#      vertex.shape = ifelse(V(sub.g.ax.2)$label %in% oral, "square", "circle"),
#      vertex.label.dist=1.2,
#      vertex.label.degree = 1.52*pi,
#      vertex.label.font = 3,
#      vertex.label.color = "black")
# # # 
# coords <- tk_coords(29)
# write_tsv(data.frame(coords), './assoc_diff/ax_coords.tsv')

#--------plot them------------#
coords <- read_tsv('./assoc_diff/ax_coords.tsv') %>% as.matrix()
svg(file="./ax-network.svg", width= 10, height=4)
par(mfrow=c(1,2), mar=c(0,0,1,0))
plot(sub.g.ax.2, 
     edge.width = E(sub.g.ax.2)$weight,
     # layout = layout.fruchterman.reingold(sub.g.ax.2),
     layout = coords,
     vertex.size = set_nodesize(net_derm_ax$normCounts2, sub.g.ax.2),
     vertex.shape = ifelse(V(sub.g.ax.1)$label %in% oral, "square", "circle"), 
     vertex.label.dist=1.1, 
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
     main = "Ax-2"
     
     )
plot(sub.g.ax.1,
     edge.width = E(sub.g.ax.1)$weight,
     # layout = layout.fruchterman.reingold(sub.g.ax.1),
     layout = coords,
     vertex.size = set_nodesize(net_derm_ax$normCounts1, sub.g.ax.1),
     vertex.shape = ifelse(V(sub.g.ax.1)$label %in% oral, "square", "circle"),
     vertex.label.dist=1.1,
     vertex.label.cex = 1.4,
     vertex.label.degree = 1.52*pi,
     vertex.label.font = 3,
     vertex.label.color = "black",
     main = "Ax-5"
     )
dev.off()
```

